---
title: "cgrRNA Pipeline"
output:
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 5
    fig_height: 5
    dev: jpeg
---

```{r include = FALSE}
require(tidyverse); require(rmarkdown); require(knitr); require(sevenbridges); 

options(max.print = "99"); opts_knit$set(width = 99)
opts_chunk$set(cache=FALSE, tidy=FALSE)

```

This project represents the current pre-release and actively developed comprehensive RNA-seq analysis pipeline used at the Cancer Genomics Research Laboratory. It is a work in progress. The goal is to document the tools and workflows that our analysts currently use, make them portable and share with the community.
  
Modules Included 
  
  * Alignment and QC
  * Differential Expression
  * Fusions (with concordance to WGS data)
  * miRNA
  * RNA Variant Calling

Tools will be described in the common workflow language and have have associated docker images hosted in the cgrlab docker registry. CWL and Docker are not a requirement to run any of the workflows.
Portability will demonstrated by using several framework/executors depending on the environment. Potential options include Rabix, Toil, SevenBridges, SnakeMake...etc.




# Alignment and QC

## STAR Alignment Workflows

```{r child = '~/cgrRNA/modules/alignment_and_qc/star_alignment/Readme.Rmd'}
```


# Fusions

## Data harmonization

### File naming conventions

All fusion output files follow the same naming schema which is the concatenation of the Sample ID, Fusion tool name, and then file extension.
 
e.g. SA01234_chimerascan_output.bedpe, SA01234_ericscript_output.txt
 
All files will be tab delimited.

## Fusion Finders

### Chimerascan

```{r child = '~/cgrRNA/modules/fusions/chimerascan/Readme.Rmd'}
```

### EricScript

```{r child = '~/cgrRNA/modules/fusions/ericscript/Readme.Rmd'}
```

### Mapsplice

```{r child = '~/cgrRNA/modules/fusions/mapslice/Readme.Rmd'}
```

### Fusion Catcher

```{r child = '~/cgrRNA/modules/fusions/fusion_catcher/Readme.Rmd'}
```

### STAR Fusion

```{r child = '~/cgrRNA/modules/fusions/star_fusion/Readme.Rmd'}
```

## Summary and Utility Apps

### Multi-Fusion Tool Output Collector

```{r child = '~/cgrRNA/modules/fusions/multi_fusion_tool_output_collector/Readme.Rmd'}
```

### Fusion Output Archiver

```{r child = '~/cgrRNA/modules/fusions/fusion_output_archiver/Readme.Rmd'}
```

### Fastq Decompress and Merge

```{r child = '~/cgrRNA/modules/fusions/fastq_decompress_and_merge/Readme.Rmd'}
```

### Combine EricScript Fusion Lists

```{r child = '~/cgrRNA/modules/fusions/combine_EricScript_fusion_lists/Readme.Rmd'}
```

