---
title: "cgrRNA Fusions Module"
output:
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 5
    fig_height: 5
    dev: jpeg
---

```{r include = FALSE}
require(tidyverse); require(rmarkdown); require(knitr); require(sevenbridges); 

options(max.print = "99"); opts_knit$set(width = 99)
opts_chunk$set(cache=FALSE, tidy=FALSE)

source("~/cgrRNA/scratch/cgc_auth.R")

```

# Data harmonization

## File naming conventions

All fusion output files follow the same naming schema which is the concatenation of the Sample ID, Fusion tool name, and then file extension.
 
e.g. SA01234_chimerascan_output.bedpe, SA01234_ericscript_output.txt
 
All files will be tab delimited.

# Fusion Finders

## 1. Chimerascan

```{r child = '~/cgrRNA/fusions/workflows/chimerascan/Readme.Rmd'}
```

## 2. EricScript

```{r child = '~/cgrRNA/fusions/workflows/ericscript/Readme.Rmd'}
```

## 3. Mapsplice

```{r child = '~/cgrRNA/fusions/workflows/mapslice/Readme.Rmd'}
```

## 4. Fusion Catcher

```{r child = '~/cgrRNA/fusions/workflows/fusion_catcher/Readme.Rmd'}
```

## 5. STAR Fusion

```{r child = '~/cgrRNA/fusions/workflows/star_fusion/Readme.Rmd'}
```

# Summary and Utility Apps

## Multi-Fusion Tool Output Collector

```{r child = '~/cgrRNA/fusions/workflows/multi_fusion_tool_output_collector/Readme.Rmd'}
```

## Fusion Output Archiver

```{r child = '~/cgrRNA/fusions/workflows/fusion_output_archiver/Readme.Rmd'}
```

## Fastq Decompress and Merge

```{r child = '~/cgrRNA/fusions/workflows/fastq_decompress_and_merge/Readme.Rmd'}
```

## Combine EricScript Fusion Lists

```{r child = '~/cgrRNA/fusions/workflows/combine_EricScript_fusion_lists/Readme.Rmd'}
```

